### 2021-02-25 quant_estimate/pse_quant_algo.tex
Draft-1 : PSE Quant Test Algo

	// case 1
	if (a > 50)	{
		c = a + 75;
	}	else	{
		c = a - 75;
	}

	// case 2
	if (d > 60)
		d = 250;

@@

	return 0;
}
\end{lstlisting}
\begin{algorithm}
    \caption{Complex Case : (Testing Based Estimation)}
    \begin{algorithmic}[1]
        \ForEach{$a \in A$}%
        \State command \algorithmiccomment{This is a comment}
        \State another command \algorithmiccomment{This is another comment}
        \EndForEach
    \end{algorithmic}
\end{algorithm}

>>>>

	// case 1 -> Pure Forall Predicate
	if (a > 50)	{
		c = a + 75;
	}	else	{
		c = a - 75;
	}

	// case 2 -> Pure PSE Predicate
	if (d > 60)
		d = 250;

@@

	return 0;
}
\end{lstlisting}

\begin{algorithm}
    \caption{Complex Case : (Testing Based Estimation)}
    \begin{algorithmic}[1]
        \ForEach{$p \in Paths$}%
        \State c := ConstraintSet(p) \algorithmiccomment{Path Constraints for p}
        \State m := Solve(c) \algorithmiccomment{solution for the path constraints}
        \State forallConcreteSet = \{ \}
        	\ForEach{$v \in ForallVars(p)$}%
        	\State concreteSet.append(\{key : v, val : m[v]\}) \algorithmiccomment{forall values}
        	\EndForEach
        \State executeCV(program, concreteSet, c)
        \EndForEach
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
	\caption{Complex Case : (k-samples)}
	\begin{algorithmic}[1]
		\ForEach{$p \in Paths$}%
		\State c := ConstraintSet(p) \algorithmiccomment{Path Constraints for p}
		\State m := Solve(c) \algorithmiccomment{solution for the path constraints}
		\State forallConcreteSet = \{ \}
			\ForEach{$v \in ForallVars(p)$}%
			\State concreteSet.append(\{key : v, val : m[v]\}) \algorithmiccomment{forall values}
			\EndForEach
		\EndForEach
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
	\caption{PSE Sampling Algorithm}
	\begin{algorithmic}[1]
		\Function{PSESample}{$\mathtt{x}, de, \varphi, \sigma, P, I$}
		\Let{$\delta$}{Generate an unused name for a probabilistic symbolic variable}
		\State{$P[\delta] = de$}
		\State{$I[\delta] = \{\delta\}$}
		\State{$\sigma[\mathtt{x}] = \delta$}
		\State\Return{$(\varphi,\sigma,P,I)$}
		\EndFunction
	\end{algorithmic}
\end{algorithm}
